% This is main.tex, a sample paper demonstrating the use of the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
% 
\documentclass[runningheads]{llncs}
%
% ---- Packages ----
%
\usepackage{graphicx} % enhanced support for graphics
\usepackage[obeyspaces]{xurl} % add macros for handling URLs in text
\usepackage[nohyperlinks,nolist]{acronym} % abbreviation utilities
\usepackage{listings}
\usepackage{float}
\usepackage{ntheorem}
\usepackage{amssymb}
\usepackage{footmisc}
\usepackage{footnote}
\usepackage{fourier}
\usepackage{caption}
\usepackage{longtable}
\usepackage[pdfusetitle]{hyperref}

\usepackage[
    type={CC},
    modifier={by},
    version={4.0},
]{doclicense}

\renewcommand{\texttt}[1]{{\renewcommand\UrlFont{\ttfamily}\nolinkurl{#1}}}

% \theoremseparator{:}
% \theorempreskip{1em}
\newtheorem{hypothesis}{Hypothesis}
\renewcommand{\thehypothesis}{H\arabic{hypothesis}}

\setlength{\tabcolsep}{3pt}
\setlength{\textfloatsep}{0.1cm}

% From https://tex.stackexchange.com/questions/192994/writing-roman-numbers-in-equation
\newcommand{\RN}[1]{%
  $\textup{\uppercase\expandafter{\romannumeral#1}}$%
}

\captionsetup[table]{skip=10pt}

% TODO: add more packages below if necessary
%
% ---- Acronyms ----
%
\begin{acronym}
\acro{rq}[RQ]{Research Question}
\acro{rts}[RTS]{Regression Test Selection}
\acro{tap}[TAP]{Test Automation Platform}
\acro{poc}[PoC]{Proof of Concept}
\acro{di}[DI]{Dependency Injection}
\end{acronym}

% 
% ---- Begin Document ----
%
\begin{document}
%
\title{The Unsafety in Java Regression Test Selection and its Occurrence in the Wild}
%
\titlerunning{The Unsafety in Java RTS and Its Occurrence in the Wild}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
% ---- Author Information ----
%
\author{Lukas Döllerer}
\institute{Seminar: Software Quality\\
  Technical University of Munich\\
  \email{lukas.doellerer@tum.de}}
%
\maketitle % typeset the header of the contribution
%
% ---- Abstract ----
%
\begin{abstract}
  Regression testing is used by developers to ensure that new
  revisions of a program do not negatively impact existing features.
  \ac{rts} excludes test cases from the regression test set. An \ac{rts}-tool that correctly
  selects all tests affected by introduced changes is
  called \emph{safe}. Prior research has shown that this safety is hard to achieve.
  Undetected unsafety can be caused by a faulty implementation or imperfect
  methodology of an \ac{rts}-tool. In this study, we collected known and discovered new unsafety
  in the popular open source \ac{rts}-tools \emph{Ekstazi}, \emph{GIBstazi}, \emph{OpenClover}, \emph{STARTS} and \emph{HyRTS}.
  We compared the tools with each other, based on reference projects that simulate sources of unsafety.
  To confirm the relevance of the discovered unsafety, we performed a broad analysis of its occurrence on a
  selection of the 100 most popular Java
  repositories on the GitHub platform. We were able to document 10 hypothetical scenarios that cause unsafe
  behavior of the examined \ac{rts}-tools. These scenarios include reflections, dependency injection, problems with runtime instrumentation
  and external files. All examined tools acted unsafe. Sources of unsafety were
  found in 88 out of the 100 scanned repositories. This leads us to the conclusion that none of the
  examined tools are currently ready to be safely used in production environments. Further research must combine
  existing knowledge and tools to develop and maintain an up-to-date implementation of \ac{rts} for Java.
  \keywords{Regression Test Selection \and Unsafety \and Java}
\end{abstract}
%
% ---- Text Parts ----
%
\input{text/01_introduction}
\input{text/02_related_work}
\input{text/03_approach}
\input{text/04_evaluation}
\input{text/05_discussion}
\input{text/06_threats_to_validity}
\input{text/98_conclusion}
%
% ---- Appendix ----
%
\appendix
\input{text/99_appendix}
%
% ---- Bibliography ----
%
\clearpage
\bibliographystyle{splncs04}
\bibliography{library.bib}
%
\clearpage
\vspace*{\fill}
\doclicenseThis
\end{document}


% TODO:
% - Tenses?
% - we too much?
% - Cite paper that evaluates starts, ekstazi and openclover and finds bugs in related work!
% - comparison of the tools, where? 
% - inline code
% - hyrts implementation missing -> super hard to find stuff -> security by obscurity.
% - Java 8 vs 1.8?
